Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-23 summary.Rmd
started writing the discussion section

>>>>

This paper shows the connection between the PABM and the GRDPG, namely that 
a PABM graph can be represented as a union of orthogonal subspaces in an 
embedding under the GRDPG framework. We then exploited this relationship to 
develop community detection and parameter estimation methods. In fact, we can 
represent any graph with Bernoulli edges as a GRDPG, and in the PABM case, 
it turns out that this relationship leads to a very straightforward 
applications of previous work from \citeauthor{rubindelanchy2017statistical}, 
\citeauthor{soltanolkotabi2012}, and \citeauthor{pmlr-v28-wang13}, which lead 
to asymptotically correct solutions with high probability. Similar methods can 
be applied for other models, such as the Nested Block Model
\cite{noroozi2021hierarchy}.
